IFC Inside: A General Approach to Retrofitting Languages with Dynamic Information Flow Control

### 2014-07-08 paper/real.tex

\subsubsection{Server-side embedding: Node.js}

@@

While the described system implements |specLangJS seqf|, server-side
applications may require access to the file system, HTTP server, HTTP
client, or other APIs that have external effects.
%
Exposing the Node.js APIs directly to sandboxed tasks is unsafe, and
thus we
%
instead implement libraries such as a labeled file system as
message exchanges between the sandboxed tasks (e.g., \textsf{task-1}
in Figure~\ref{fig:node}) and the main Node.js task that implements
our IFC monitor.\footnote{
  Importantly, we provide mostly-identical interfaces to
  the standard Node.js libraries, hiding the underlying
  message-passing implementations.
}
%
This is safer than the approach of simply wrapping objects, which can
potentially allow objects to be accessed outside the context.
%
This task is trusted to ensures that labels are
propagated to files and the labels of the task and the file in question permit
this flow.
%
Unfortunately, while imposing such a proof burden on the
framework developer is undesirable, this also has to be expected:
different language environments expose different libraries for
handling external I/O, and the correct treatment of external effects
is application specific.
%
For instance, in the case of Node.js, how labels interact with the
file system may even vary according to the application (e.g.,
in the IFC system Hails~\cite{hails}, labels are not persisted).
%
%While we can extend our formalism to model a particular interface to
%the file system, HTTP client, etc. the utility of this formalization is
%unclear and left to future work.
%

\subsubsection{Client-side embedding: Gecko}

We now describe some of the implementation aspects of
COWL~\cite{swapi}, for which this work serves as the theoretical
underpinning.
%
Since the architecture of COWL is similar to that of Node.js, we focus
on the main differences.

Tasks in COWL usually correspond to browsing contexts, such as iframes,
where the global object |tS0| also contains the DOM, the
\verb|XMLHttpRequest| (XHR) object, etc.
%
Existing browser APIs also offer \emph{web workers}, which can
be spawned by JavaScript code and have
the same isolation properties as tasks in our system.
%
The isolation of web workers was motivated by the lack of multithreading
in JavaScript; however, their isolation properties are equally useful for information
flow control.

To ensure that JavaScript code cannot communicate using these objects
(e.g., to the network with XHR or persistent storage using the DOM),
COWL additionally uses content security policy (CSP)~\cite{csp1.1}.\footnote{
  Since CSP does not yet restrict message-passing or navigation, this
  was addressed explicitly.
}
%
Note, that this does not prevent tasks from manipulating the DOM
(e.g., to render information), so external effects due to DOM access
are also suppressed.
%
Simply disallowing all external effects for all browsing contexts is
overly-restricting; pages typically load images, perform XHR requests,
etc.
%
Hence, COWL allows
controlled network communication (inter-frame communication is
dictated by our |send| rule) by associating an implicit label with a
remote host: namely the label corresponding to its origin.
%
In turn, when a task perform a request, the COWL runtime performs the
same label check as that of |send|, e.g., does the task label flow to
the remote origin label.

Once again, while the external effects of COWL can be formally modeled,
we do not model these effects in our more general framework, since, like
for Node.js case, they are a platform-specific
detail.
%
Indeed, even the labeled HTTP client in  Node.js and COWL differ, even
though they're both JavaScript systems, simply because of the
differing environments.

>>>>

\subsubsection{Server-side IFC: Node.js}

@@

While the described system implements |specLangJS seqf|, server-side
applications may require access to the file system, HTTP server, HTTP
client, or other APIs that have external effects.
%
Exposing the Node.js APIs directly to sandboxed tasks is unsafe, and
thus we
%
instead implement libraries such as a labeled file system as
message exchanges between the sandboxed tasks (e.g., \textsf{task-1}
in Figure~\ref{fig:node}) and the main Node.js task that implements
our IFC monitor.\footnote{
  Importantly, we provide mostly-identical interfaces to
  the standard Node.js libraries, hiding the underlying
  message-passing implementations.
}
%
This is safer than the approach of simply wrapping objects, which can
potentially allow objects to be accessed outside the context.
%
This task is trusted to ensures that labels are
propagated to files and the labels of the task and the file in question permit
this flow.
%
Unfortunately, while imposing such a proof burden on the
framework developer is undesirable, this also has to be expected:
different language environments expose different libraries for
handling external I/O, and the correct treatment of external effects
is application specific.
%
For instance, in the case of Node.js, how labels interact with the
file system may even vary according to the application (e.g.,
in the IFC system Hails~\cite{hails}, labels are not persisted).
%
%While we can extend our formalism to model a particular interface to
%the file system, HTTP client, etc. the utility of this formalization is
%unclear and left to future work.
%
We do not extend our formalism to account for the  particular
interface to the file system, HTTP client, etc., as this is
specific to the Node.js implementation and does not generalize
to other systems.

\subsubsection{Client-side IFC: Gecko}

We now describe some of the implementation aspects of
COWL, a JavaScript implementation of coarse-grained
IFC for Mozilla's Gecko.  This work provides the formal basis for
the implementation, and COWL is described in much more detail in~\cite{swapi}.
%
Since the architecture of COWL is similar to that of Node.js, we focus
on the main differences.

%Tasks in COWL  correspond to browsing contexts, such as iframes,
%where the global object |tS0| also contains the DOM, the
%\verb|XMLHttpRequest| (XHR) object, etc.
%
Existing browser APIs offer \emph{web workers}, which can
be spawned by JavaScript code and have
the same isolation properties as tasks in our system.
%
The isolation of web workers was motivated by the lack of multithreading
in JavaScript; however, their isolation properties are equally useful for information
flow control.

To ensure that JavaScript code cannot communicate using the global object
(e.g., to the network with XHR or persistent storage using the DOM),
COWL additionally uses content security policy (CSP)~\cite{csp1.1}.\footnote{
  Since CSP does not yet restrict message-passing or navigation, this
  was addressed explicitly in the implementation.
}
%
Note, that this does not prevent tasks from manipulating the DOM
(e.g., to render information), so external effects due to DOM access
are also suppressed.
%
Simply disallowing all external effects for all browsing contexts is
overly-restricting; pages typically load images, perform XHR requests
to dynamically load data,
etc.
%
Hence, COWL allows
controlled network communication (inter-frame communication is
dictated by our |send| rule) by associating an implicit label with a
remote host: namely the label corresponding to its origin.
%
In turn, when a task perform a request, the COWL runtime performs the
same label check as that of |send|, namely that the task label can
flow to
the remote origin label.

Once again, while the external effects of COWL can be formally modeled,
we do not model these effects in our more general framework, since, like
for Node.js case, they are application specific.
%
%Indeed, even the labeled HTTP client in  Node.js and COWL differ, even
%though they're both JavaScript systems, simply because of the
%differing environments.
